% Copyright page

\begin{narrowsection}{155mm}{left}
{\small
\setlength{\parindent}{0em}\setlength{\parskip}{1em}

~

\vfill

Denna bok får kopieras, spridas, ombearbetas, och användas i enlighet med MIT-licensen nedan.

\textit{Copyright \copyright{} \copyrightyear{} \authorname}

\textit{Permission is hereby granted, free of charge, to any person obtaining a copy of this book and associated documentation files (the "Book"), to deal in the Book without restriction, including without limitation the rights to use, copy, modify, merge, publish, distribute, sublicense, and/or sell copies of the Book, and to permit persons to whom the Book is furnished to do so, subject to the following conditions:}

\textit{The above copyright notice and this permission notice shall be included in all copies or substantial portions of the Book.}

\textit{THE BOOK IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE BOOK OR THE USE OR OTHER DEALINGS IN THE BOOK.}

Verkliga platser och historiska personer kan förekomma i den här boken. Alla händelser är däremot uppdiktade. Ingen nu levande människa finns återgiven. Alla eventuella likheter med nu levande personer är antingen slumpmässiga, eller kopplade till historiska personer.

Copyright \copyright{} \copyrightyear{} \authorname

Första utgåvan, \editionyear{}

ISBN \isbn{}

Publicerad av \publisher{}
}
\end{narrowsection}
